%\section{THEORICAL EXPLANATION}\label{sec:cone}
\section{Introduction}\label{sec:int} 


{\bf The text should be updated to address the following items discussed in the meeting.}

2 [Dr. Paktinat] Introduction 

2.1 Theorical explanation {\bf Done}

2.1.1 Wprime introduction {\bf Done}

right-left handed {\bf Done}

2.1.2 experimental results {\bf Done}

2.1.3 motivate DiWPrime production

2.1.4 Motivate to tau decay

2.2 explain this study {\bf Done}

2.2.1 using the cms ditau results and interpret it {\bf Done}




New heavy charged gauge bosons, called \wprime bosons, are predicted by numerous different extensions of the standard model of the elementary particles (SM). 
The SM W boson couples only to left-handed fermions, whereas the coupling of \wprime boson could be completely left-handed, right-handed or a mixture of both. 

The general form of the lagrangian describing the fermionic interactions of \wprime boson is given in  Ref.~\cite{Sullivan:2002jt}
\begin{eqnarray}
{\cal L}& =& \frac{V_{ij}}{2\sqrt{2}}\bar{f_i} \gamma_{\mu}(g^\prime_{R_{i,j}} (1+{\gamma}^5)+
g^\prime_{L_{i,j}}
(1-{\gamma}^5)) W^{\prime \mu} f_j  \nonumber\\
&+& \mathrm{h.c.},
\end{eqnarray}
where $g'_{R(L)_{i,j}}$ are right handed (left-handed) coupling constants. The $V'_{i,j}$ matrix refers to a $3\times3$ identity matrix for leptons and the CKM matrix for quarks. The $(1\pm{\gamma^5})$ operators represent left and right-handed chiral projection operators. In the case, $g'_R = 0$ and $g'_L \neq 0$ (pure left-handed), both leptons and quarks can couple to \wprime boson, but where $g'_R \neq 0$ and $g'_L = 0$ (pure right-handed) only quarks can couple to \wprime boson, because we either do not introduce right-handed neutrinos or they are assumed to be much heavier than \wprime boson. 

In this paper, we consider a situation where two opposite-sign \wprime bosons are produced. Each of them decays to a $\tau$ lepton and its neutrino ($\nu_{\tau}$). The $\tau$ lepton decays hadronically $(\tau_h)$  or leptonically (e or $\mu$). The branching ratios of these decays are 65\%, 17\% and 17\%, respectively. Since we ask for two $\tau$ leptons in the final state, $g'_L$ can not be zero. 
We use the efficiencies provided by the CMS experiment \cite{Khachatryan:2016trj} to find the yields of our favorite signal and compare it with the reported SM backgrounds to set lower limit on the mass of \wprime boson. 
The CMS analysis uses LHC data from proton-proton collisions at a center-of-mass energy of 8 TeV to search for new physics in di-tau final states.  The data corresponds to an integrated luminosity of 18.1 and 19.6 $fb^{-1}$ in different channels. Three different final states are considered depending on the decay of two $\tau$ leptons, fully hadronic $(\tau_h \tau_h)$, where both $\tau$ leptons decay hadronically and $\ell\tau_h$ (e$\tau_h$ or $\mu\tau_h$), where one $\tau$ lepton decays hadronically and the other decays leptonically. The schematic diagram of decay is shown in figure 1.{\bf should be fixed by ref.}

In different experiments, many searches are done to see the signatures of \wprime boson, but up to now all of them have failed. The most stringent limit is set by the ATLAS experiment in an analysis which looks at the tail of the lepton transverse mass distribution \cite{ATLAS:2016ecs}. The lepton is assumed to be produced in the decay of a \wprime boson associated with missing transverse energy coming from a neutrino. It has excluded the \wprime boson with masses smaller than 4.74 TeV at a 95\% confidence level (CL), assuming a pure left-handed \wprime boson with $g'_L$ equal to the coupling of the SM W boson. 